# rituals {#rituals}

## instantiate

Ask albert to instantiate.

Start each [day](https://study.com/academy/lesson/german-days-of-the-week.html) by drawing up a [day view](#day-view).

Begin the daily log, and add priority ($*$) [daily tasks](#daily-tasks).

[`review`](#review).


## day view {#day-view}

todo: port in googlesheet instead of hardcoding this

tracker | position | description
- | - | -
goals | top left | pom goals
poms | next to goals | track poms achieved
projects | top right| one project/category
[order of events](#order-of-events) | below goals | live with intent
task cycles | below projects | $\varphi, \theta, \psi, \overline o$

Add 


## daily tasks {#daily-tasks}

### $*$

```{r priority tasks, echo=FALSE}
daily_tasks %>% 
  filter(priority == "$*$") %>% 
  knitr::kable()

```

### $\sim$

```{r anxiety tasks, echo=FALSE}
daily_tasks %>% 
  filter(priority == "$\\sim$") %>% 
  knitr::kable()

```

### $\varnothing$

```{r nullset tasks, echo=FALSE}
daily_tasks %>% 
  filter(priority == "$\\varnothing$",
         category != "$\\pi$") %>% 
  knitr::kable()

```


### $\pi$


```{r pi, echo=FALSE}
daily_tasks %>% 
  filter(category == "$\\pi$") %>% 
  knitr::kable()

```


## email

### process

 Check inbox once a day.
 
 - archive [and label] emails that don't require actions
 - if I know what I want to say, best to do it now
 - if it's going to be lengthy or $\sim$, label as `needs action` 
 
### needs action

- start from the bottom, gmail doesn't sort descending
- write a next action
- migrate task to $\sim$ [todo: quaver] $+ \sim$
- can stop after one pom on this each day

## **`review`** {#review}

### daily log

This is the hard part.

Pare down to one active project per category and process daily list to end of log. 

Cross through actions above. 

#### if this project will take more than a day

- if ($*$) or ($\sim$), create project for next step and migrate to projects waiting to progress
- else if associated with a repo, migrate to issues 
- else migrate to [monthly log](#monthly-log)

- add [signifiers](#signifiers) 
- log projects in [day view](#day-view) tracker
- add projects from [monthly log](#monthly-log) if all $*$ and $\sim$ have been completed
- aim to progress at least one $*$ from the [monthly log](#monthly-log)

### day view

This is the sparkjoy bit.

- count poms
- log goals
- top up projects from [projects waiting](#projects-waiting) to maximum three active projects, one per category
- assign task cycles
    - exclude $\varnothing$ categories with no $*$ and $\sim$ projects where current goal has already been met in poms by category
    - always finish with scheduling review $\overline o$
    - consider including a [sparkjoy](https://en.wikipedia.org/wiki/Marie_Kondo) project
    
### assess 

plan poms and $\pi$ to next goal

Calculate number of poms I can realistically do, the floor of 
$$
14 - t - \frac 3 2 c
$$
where $t$ denotes the number of hours of travel, and $c$ the number of hours of _community_, where the lattter includes teaching, outreach, and research collaborations. That, is I aim to draw a distinction between self-directed time, and time where I have the benefit of external motivations.

```{r }
# todo: import tidyverse into dontpanic

library(tidyverse)

# output as of this update

# todo: add dataset arg to fn

dontpanic::calculate_pom_goal(
  travel_hrs = 0, # no travel today
  community_hrs = 0 # no teaching, meetings today
)


```



### minibreak peeps

- social media & slack

## task cycle

shorthand | description
- | -
$\forall *$ | complete all priority ($*$) tasks
$\sim \geqslant 1$ | complete at least one anxiety ($\sim$) task
$\varnothing \geqslant 0$ | complete any or none of the untagged tasks 
$\cdot \geqslant 1$ | write down as many next actions as I can think of
$\overline o$ | [review](#review)

## monthly log {#monthly-log}

List of projects that will take longer than a day.

## pom goals

pom := 20 minutes

```{r echo=FALSE}
measures %>% pluck("data", "workload_key") %>% 
  select(-phi_hrs, -theta_hrs, -psi_hrs, -exercise_hrs) %>% 
  knitr::kable()

```

## order of events {#order-of-events}

Day begins with [review](#review) $\overline o$.

### workday

Alternate events:

- $\not n + 2$ poms
- $\pi$

Around other events such as meetings. 

### wake up

- wake up
- [read]
- wash & dress
- [yoga]
- [day view]{#day-view}
- [yoga]

### evening

- bathtime + reading
- bed

## signifiers {#signifiers}

> todo: create a signifiers sheet

```{r  echo=FALSE}
measures %>% 
  pluck("data", "signifiers") %>% 
  mutate(signifier = paste0("$", signifier, "$")) %>% 
  knitr::kable()

```

## playlists

### for the good days

<iframe src="https://open.spotify.com/embed/user/acgray101/playlist/3dAEbZZlfN3qoZKbJdwFBE" width="300" height="380" frameborder="0" allowtransparency="true" allow="encrypted-media"></iframe>

### for the not so good days

<iframe src="https://open.spotify.com/embed/user/acgray101/playlist/5koDEJPBsLsLPDxBKKAh7F" width="300" height="380" frameborder="0" allowtransparency="true" allow="encrypted-media"></iframe>