# rituals {#rituals}

## instantiate

Start each [day](https://study.com/academy/lesson/german-days-of-the-week.html) by drawing up a [day view](#day-view).

Begin the daily log, and add priority ($*$) [daily tasks](#daily-tasks).



## day view {#day-view}

tracker | position | description
- | - | -
poms | top left | track poms achieved
goals | below poms | pom goals
projects | top right| one project/category
task cycles | below projects | $\varphi, \theta, \psi, \overline o$
[order of events](#order-of-events) | below goals | live with intent


## daily tasks {#daily-tasks}

```{r daily tasks all, echo=FALSE}
daily_tasks <- measures %>% 
  pluck("data", "daily_tasks") %>% 
  mutate(context = paste0("$", context, "$"),
         priority = paste0("$", priority, "$"),
         category = paste0("$", category, "$")) %>%
  arrange(priority, context, category) 

daily_tasks %>% 
  knitr::kable()
```

### $\pi$

```{r pi, echo=FALSE}
daily_tasks %>% 
  filter(category == "$\\pi$") %>% 
  knitr::kable()


```


## review {#review}

### daily log

Pare down to one active project per category and process daily log:

- migrate to GitHub issues or [monthly log](#monthly-log)
- add [signifiers](#signifiers) 
- log projects in [day view](#day-view) tracker
- add projects from [monthly log](#monthly-log) if all $*$ and $\sim$ have been completed

### day view

- count poms
- log goals
- assign task cycles
- +2 events to [order of events](#order-of-events)

### minibreak peeps

- social media & slack

## monthly log {#monthly-log}

List of projects that will take longer than a day.

## pom goals

pom := 20 minutes

```{r echo=FALSE}
measures %>% pluck("data", "workload_key") %>% 
  select(-phi_hrs, -theta_hrs, -psi_hrs, -exercise_hrs) %>% 
  knitr::kable()

```

## order of events {#order-of-events}

Day begins with [review](#review) $\overline o$.

### workday

Alternate events:

- $\not n + 2$ poms
- $\pi$

Around other events such as meetings. 

### wake up

- wake up
- [read]
- dress
- wash
- [yoga]
- [day view]{#day-view}
- [yoga]

### evening

- bathtime + reading
- bed


## signifiers {#signifiers}

> todo: create a signifiers sheet

```{r  echo=FALSE}
measures %>% 
  pluck("data", "signifiers") %>% 
  mutate(signifier = paste0("$", signifier, "$")) %>% 
  knitr::kable()
```