---
title: "writeflow"
description: |
  Workflow for writing across the manuscript.
author:
  - name: Charles T. Gray 
    url: https://softloud.github.io/onetimetrophybitch/about.html
date: "updated: `r Sys.Date()`"
output: 
  distill::distill_article:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
# packages used 
library(tidyverse)
library(kableExtra)

replace_na <- function(text) {
  if_else(is.na(text), "", text)
}

map_na <- function(vector_text) {
  map_chr(as.character(vector_text), replace_na)
}

tracker <- read_rds("data/writing_tracker.rds")

tracker[2:ncol(tracker)] <- tracker[2:ncol(tracker)] %>% 
  as.list() %>% 
  map(map_na) %>% 
  as_tibble()

headings <- names(tracker) %>% 
  as.character()

names(tracker) <- 
  names(tracker) %>% str_sub(1, 4)

```


# Three dots for three manuscripts

[Instantiate](#instantiate), at the beginning, thereafter turn to writing tracker. 

Count completed sections, and estimate how much of the manuscript has been completed. Add three to that and set this as the **goal** for the day. 

Set **n = 3**.

1. Randomly select three manuscripts. Randomly select **n** sections (for each manuscript) from those with the least number of dots in their corresponding row in the writing tracker. 

```{r}
# for example
tracker %>% 
  mutate(# head = rep("x", 3),
         # sent = c("x", "", "x"),
         para = c("x", "", "")) %>% 
  kable() 

```


2. Write as separate tasks in bullet journal. 

3. Actioning one of these means attempting to complete one dot: heading, sentence, paragraph, etc. 

4. Cross action as complete when completed, or if the pomodoro runs out. Consider adding subsections to tracker if action incomplete.

5. If **goal** is not met for manuscript, set **n = goal - number of poms completed** for this manuscript.  If **goal** is met, stop and switch to next manuscript. If third manuscript, only continue for fun. 

# Instantiate writing tracker table {#instantiate} 

Set three sections before beginning, as any piece of scientific writing  will have an introduction, motivating content, content section, doing the science, and conclusion of content's findings. 

```{r}

tracker %>% 
  kable() 

```




